---
output: pdf_document
mainfont: Arial
sansfont: Arial
fontsize: 12pt
---


```{r setup, include=FALSE}
#' Development
#' 5.20.22 Just started making notes on changes. Updated export of exercise prescription in minutes block to only be on Mondays and added lubridate to libraries
#' 9.27.22 Added conditional statment warning pt of reduction in trainers JC

library(tidyverse)
library(htmlTable)
library(knitr)
library(rio)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)

###### Build Root Server #####  
if(Sys.info()["nodename"]=="workstation_1" & Sys.info()["user"]=="study_coordinator_2") {
  root_p <- file.path("drive")
  root_server_dir <- file.path(root_p,"study_dir_a")
  python_cmd_prefix <- "py "
} else if(Sys.info()["nodename"]=="workstation_3" & Sys.info()["user"]=="root"){
  root_p <- ""
  # root_server_dir <- file.path(root_p,"ADC_Data")
  root_server_dir <- file.path(root_p,"COMET")
  python_cmd_prefix <- "python "
}
  

###### Load Directories #####
load(file.path(root_server_dir,'study_dir_a','COMET','data','clean','directories.Rdata'))


load(file.path(data_dir,'participant_email','current_participant.Rdata'))

logo <- file.path(data_dir,'participant_email','COMETLogo.jpg')


```

\begin{center}

  \includegraphics[width = 2cm, height = 2cm]{`r logo`}

\end{center}


# `r current$scrn_fname` `r current$scrn_lname`'s Week `r current$presentweeknum` Exercise Prescription


```{r mintues, include=FALSE}

  week <- current$presentweeknum

  endurance_progression <- current_exercise_prescription$aerobic_duration
  
  pt_sessions <- case_when(week <= 26 ~ 3,
                           week > 26 & week <= 36 ~ 2,
                           week > 36 ~ 1)
  
  unsupervised_sessions <- case_when(week == 1 ~ 0,
                                     week == 2 ~ 0,
                                     week == 3 ~ 0,
                                     week == 4 ~ 1,
                                     week == 5 ~ 1,
                                     week == 6 ~ 2,
                                     week > 6 ~ 5-pt_sessions)
  
  #removed supervised and independent time from prescription on 1.24.22
  supervised_time <- NA #case_when(week <= 1 ~ 60,
                            #   week == 2 ~ 75,
                            #  week == 3 ~ 90,
                            # week >= 4 & week <= 26 ~ 90,
                            # week > 26 & week <= 36 ~ 60,
                            # week > 36 ~ 30)
  
  
  independent_time <- NA #endurance_progression - supervised_time
  
  min <- current_exercise_prescription$hrr_min
  max <- current_exercise_prescription$hrr_max
  
  prescription_df <- data.frame(current$comet_study_id, as.numeric(week), endurance_progression, pt_sessions, supervised_time, independent_time, min, max, unsupervised_sessions)
  
  if(file.exists(file.path(data_dir,'participant_email','sent_prescriptions',paste0('146904_',current$comet_study_id,'.csv')))==T) {
    
    prescription_record <- import(file.path(data_dir,'participant_email','sent_prescriptions',paste0('146904_',current$comet_study_id,'.csv')))
    prescription_record <- bind_rows(prescription_record, prescription_df)
    
    if(wday(today()) == 2){
      export(prescription_record, file.path(data_dir,'participant_email','sent_prescriptions',paste0('146904_',current$comet_study_id,'.csv')))
    }    
  } else {
    export(prescription_df, file.path(data_dir,'participant_email','sent_prescriptions',paste0('146904_',current$comet_study_id,'.csv')))
  }
  
  

```
`r if(week == 25 | week == 26){paste0("In ",27-week," week(s) you will change to working with your trainer twice per week. Your total exercise goals will not change. We suggest having a conversation with your traner to prepare for this change.")}`

`r if(week == 35 | week == 36){paste0("In ",37-week," week(s) you will change to working with your trainer once per week. Your total exercise goals will not change. We suggest having a conversation with your traner to prepare for this change.")}`

**Target Total Weekly Exercise Minutes:** `r endurance_progression` minutes

**Target Heart Rate Range:** `r min` bpm - `r max` bpm

**Number of Personal Trainer Sessions:** `r pt_sessions` sessions

**Number of Unsupervised Sessions:** `r unsupervised_sessions` sessions

#### Reminders

* Remember to bring your exercise log and record your exercise immediately

* Remember to start and stop your Fitbit watch at the beginning and end of exercise sessions

* The Target Total Weekly Exercise Minutes does not include the warm-up and cool-down time.

* Walking is the encouraged mode of exercise either using a walking track or treadmill. However, you are allowed to use other types of endurance exercise equipment. Acceptable modes of exercise include but are not limited to the following: 
  + Bike (Upright, Recumbent, or Airdyne) 
  + Elliptical 
  + Rower 
  + Stair Climber or Stepper (Upright or Recumbent)


* You may do a maximum of 60 minutes in any session and spread out the target total exercise minutes over no less than 3 days a week, and preferably no more than 5 days.

*  Ideally, you will reach 30 minutes per session by the third week of the intervention and this will be maintained for the duration of the intervention. 

* Exercise Session Flow
  + 3-5 minute low intensity warm-up to get heart rate into range, which is not counted toward exercise
  + Start the Fitbit and the exercise session
  + Do the exercise session
  + Stop the Fitbit and complete the exercise session
  + Complete a cooldown period and stretching

* From time to time, you may miss a supervised session due to illness, travel, or other commitments. For any missed sessions, it is important to follow some rules regarding rescheduling: 
  + A maximum of supervised sessions per week consistent with the frequency of supervised sessions at that point in the study
  + A maximum of 60 minutes per supervised session per day 


``` {r generate_html_ex_prescription, include=FALSE}

html_ex_prescription <- paste0('
                  <tr>
                     <td align="left">
                      <p style="font-family:arial;" style= "font-size:125%;"><b>',current$scrn_fname,'&#8217;s Week ',current$presentweeknum,' Exercise Prescription</b></p>
                    </td>
                  </tr>
                  <tr>
                     <td align="left">
                      <p style="font-family:arial;" style= "font-size:100%;">
                      <br><b>Target Total Weekly Exercise Minutes:</b> ',endurance_progression,' minutes<br>
                      <b>Target Heart Rate Range:</b> ',min,' - ',max,' bpm<br>
                      <b>Number of Personal Trainer Sessions:</b> ',pt_sessions,' sessions<br>
                      <b>Number of Unsupervised Sessions: </b> ',unsupervised_sessions,' sessions<br><br>
                      
                      <b>Reminders </b><br><br>
                        <ul>
                          <li>Remember to bring your exercise log and record your exercise immediately</li>
                          <li>Remember to start and stop your Fitbit watch at the beginning and end of exercise sessions</li>
                          <li>The Target Total Weekly Exercise Minutes does not include the warm-up and cooldown time.</li>
                          <li>Walking is the encouraged mode of exercise either using a walking track or treadmill. However, you are allowed to use other types of endurance exercise equipment. Acceptable modes of exercise include but are not limited to the following: </li>
                            <ul> 
                              <li>Bike (Upright, Recumbent, or Airdyne)</li>
                              <li>Elliptical </li>
                              <li>Rower</li>
                              <li>Stair Climber or Stepper (Upright or Recumbent)</li>
                            </ul>
                          <li>You may do a maximum of 60 minutes in any session and spread out the target total exercise minutes over no less than 3 days a week, and preferably no more than 5 days.</li>
                          <li>Ideally, you will reach 30 minutes per session by the third week of the intervention and this will be maintained for the duration of the intervention. </li>
                          <li>Exercise Session Flow</li>
                            <ul> 
                              <li>3-5 minute low intensity warm-up to get heart rate into range, which is not counted toward exercise</li>
                              <li>Start the Fitbit and the exercise session</li>
                              <li>Do the exercise session</li>
                              <li>Complete the exercise session then stop the Fitbit</li>
                              <li>Complete a cooldown period and stretching</li>
                            </ul>
                          <li> From time to time, you may miss a supervised session due to illness, travel, or other commitments. For any missed sessions, it is important to follow some rules regarding rescheduling:</li>
                            <ul>
                              <li>A maximum of supervised sessions per week consistent with the frequency of supervised sessions at that point in the study</li>
                              <li>A maximum of 60 minutes per supervised session per day</li>
                            </ul>
                          </ul>
                      </p>
                    </td>
                  </tr>'
)

id_to_check <- current$comet_study_id

to_save <- c('html_ex_prescription','id_to_check')                 
save(list = to_save, file = file.path(data_dir,'participant_email','current_html_prescription.Rdata'))


```








